\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2013-01-07 smurf_paper.tex
a couple of typos

There are numerous ways to attack this map-making problem, both in
terms of the data-collection method, and processing. The two most
important principles to follow in terms of scan strategy are: (i) to
modulate the astronomical signals of interest in such a way that they
appear in the lowest-noise regions of the bolometer noise power
spectrum, i.e., above the $1/f$ knee; and (ii) to provide good
``cross-linking'', in which each portion of the map is scanned at a
range of position angles, again, to help distinguish time-varying
noise features from fixed astronomical sources. In the case of \scuba,
(i) is achieved through fast-scanning of the entire telescope (up to
600\,arcsec\,sec$^{-1}$), such that significant drift in the
bolometers due to low-frequency noise occurs more slowly than the
crossing times for the astronomical scales of interest; and (ii) by
offering scan patterns that cross the sky at a wide range of position
angles. Such methods are now used by virtually all existing
ground-based submillimetre cameras
\citep[e.g.,][]{glenn1998,weferling2002,wilson2008,kovacs2008b}, in
preference to ``chopping'' methods (where the secondary is moved
quickly to modulate the signal) that were more appropriate for older
instruments that had poorer low-frequency noise performance, and were
only sensitive to modest angular scales. We note that under some
circumstances cross-linking may not be essential. For example, SPT,
which was designed to measure CMB anisotropies, scans entirely in
azimuth \citep{schaffer2011}. While this strategy limits its ability
to recover large angular scales transverse to the scan direction, the
anisotropic filtering in its maps can be accounted for during analysis
to achieve SPTs focussed objectives \citep[in contrast, the similar
ACT experiment uses cross-linking to improve its response to
large-angular scales,][]{das2011}. This approach is less practical as
a general solution for \scuba, however, which must serve a broader
range of scientific interests.

@@

From a scientific perspective, the most important goal of map-making
is to efficiently use all of the available data to achieve the
greatest sensitivity to astrononomical sources that the instrument is
capable of. Generally speaking, only a small percentage of the data
are flagged as unusable during map-making beyond the $\sim$70\%
detector yield.  As an example, for the 450\,\micron\ scan of Uranus
that will be presented in Section~\ref{sec:point}, during
pre-processing: 31\% of the data (1587/5120 bolometers) are flagged
due to data acquisition problems (dead or deactivated bolometers, or
non-linear flatfields); 0.12\% of the data are flagged due to steps
(including a small region about the steps, Section~\ref{sec:steps});
and 0.83\% if the data are flagged because the telescope was
stationary (Section~\ref{sec:flagbadbol}). Once the iterative solution
begins: 55 spikes are detected using the map-based despiker
($1.2\times10^{-6}$ \% of the data, Section~\ref{sec:ast}); and 0.72\%
of the data are flagged as outliers compared to the common-mode
(Section~\ref{sec:comgai}).

>>>>

There are numerous ways to attack this map-making problem, both in
terms of the data-collection method, and processing. The two most
important principles to follow in terms of scan strategy are: (i) to
modulate the astronomical signals of interest in such a way that they
appear in the lowest-noise regions of the bolometer noise power
spectrum, i.e., above the $1/f$ knee; and (ii) to provide good
``cross-linking'', in which each portion of the map is scanned at a
range of position angles, again, to help distinguish time-varying
noise features from fixed astronomical sources. In the case of \scuba,
(i) is achieved through fast-scanning of the entire telescope (up to
600\,arcsec\,sec$^{-1}$), such that significant drift in the
bolometers due to low-frequency noise occurs more slowly than the
crossing times for the astronomical scales of interest; and (ii) by
offering scan patterns that cross the sky at a wide range of position
angles. Such methods are now used by virtually all existing
ground-based submillimetre cameras
\citep[e.g.,][]{glenn1998,weferling2002,wilson2008,kovacs2008b}, in
preference to ``chopping'' methods (where the secondary is moved
quickly to modulate the signal) that were more appropriate for older
instruments that had poorer low-frequency noise performance, and were
only sensitive to modest angular scales. We note that under some
circumstances cross-linking may not be essential. For example, SPT,
which was designed to measure CMB anisotropies, scans entirely in
azimuth \citep{schaffer2011}. While this strategy limits its ability
to recover large angular scales transverse to the scan direction, the
anisotropic filtering in its maps can be accounted for during analysis
to achieve SPT's focussed objectives \citep[in contrast, the similar
ACT experiment uses cross-linking to improve its response to
large-angular scales,][]{das2011}. This approach is less practical as
a general solution for \scuba, however, which must serve a broader
range of scientific interests.

@@

From a scientific perspective, the most important goal of map-making
is to efficiently use all of the available data to achieve the
greatest sensitivity to astrononomical sources that the instrument is
capable of. Generally speaking, only a small percentage of the data
are flagged as unusable during map-making beyond the $\sim$70\%
detector yield.  As an example, for the 450\,\micron\ scan of Uranus
that will be presented in Section~\ref{sec:point}, during
pre-processing: 31\% of the data (1587/5120 bolometers) are flagged
due to data acquisition problems (dead or deactivated bolometers, or
non-linear flatfields); 0.12\% of the data are flagged due to steps
(including a small region about the steps, Section~\ref{sec:steps});
and 0.83\% of the data are flagged because the telescope was
stationary (Section~\ref{sec:flagbadbol}). Once the iterative solution
begins: 55 spikes are detected using the map-based despiker
($1.2\times10^{-6}$ \% of the data, Section~\ref{sec:ast}); and 0.72\%
of the data are flagged as outliers compared to the common-mode
(Section~\ref{sec:comgai}).
